\clearpage
\addcontentsline{toc}{chapter}{References}
\bibliographystyle{unswthesis}
\begin{thebibliography}{999}

\bibitem
{intro-back}
Blei, David M. "Probabilistic topic models." Communications of the ACM 55.4 (2012): 77-84.

\bibitem
{find}
Griffiths T L, Steyvers M. Finding scientific topics[J]. Proceedings of the National academy of Sciences, 2004, 101(suppl 1): 5228-5235.

\bibitem
{corr}
Blei D M, Lafferty J D. A correlated topic model of science[J]. The Annals of Applied Statistics, 2007, 1(1): 17-35.
\bibitem
{dirbn}
Zhao, He, et al. "Dirichlet belief networks for topic structure learning." Advances in neural information processing systems. 2018.


\bibitem
{hdp}
Teh, Y. W., Jordan, M. I., Beal, M. J., & Blei, D. M. (2005). Sharing clusters among related groups: Hierarchical Dirichlet processes. In Advances in neural information processing systems (pp. 1385-1392).



\bibitem
{han}
Zhou, Mingyuan, et al. "Beta-negative binomial process and Poisson factor analysis." Artificial Intelligence and Statistics. 2012.

\bibitem
{crt}
Griffiths, Thomas L., et al. "Hierarchical topic models and the nested chinese restaurant process." Advances in neural information processing systems. 2004.

\bibitem
{bunt}
W. Buntine and A. Jakulin. Discrete component anal-
ysis. In Subspace, Latent Structure and Feature Se-
lection Techniques. Springer-Verlag, 2006.

\bibitem
{samp}
Bishop, Christopher M. Pattern recognition and machine learning. springer, 2006.

\bibitem
{mh}
Chib, Siddhartha, and Edward Greenberg. "Understanding the metropolis-hastings algorithm." The american statistician 49.4 (1995): 327-335.

\bibitem
{bda}
Gelman, Andrew, et al. Bayesian data analysis. CRC press, 2013.

\bibitem
{origin}
David M. Blei, AndrewY. Ng, Michael I. Jordan,  LatentDirichlet Allocation, Journal of Machine Learning Research 3, p993-1022,2003

\bibitem
{tcf}
Nigam, Kamal, et al. "Text classification from labeled and unlabeled documents using EM." Machine learning 39.2-3 (2000): 103-134.

\bibitem
{plsa}
Hofmann, Thomas. "Probabilistic latent semantic analysis." arXiv preprint arXiv:1301.6705 (2013).

\bibitem
{Teh}
Y.W.Teh, M. I. Jordan, M. J. Beal, and D. M. Blei. Hierarchical Dirichlet processes. Journal of the American Statistical Association, 101(476):1566–1581, 2006.

\bibitem
{Zhao}
Zhao, H., Du, L., Buntine, W., and Zhou, M. Dirichlet
belief networks for topic structure learning. In NeurIPS,
pp. 7966–7977, 2018

\bibitem
{Zhou}
Zhou, M., Cong, Y., and Chen, B. Augmentable gamma
belief networks. Journal of Machine Learning Research,
17(163):1–44, 2016.

\bibitem
{coolaps}
Liu, Jun S. "The collapsed Gibbs sampler in Bayesian computations with applications to a gene regulation problem." Journal of the American Statistical Association 89.427 (1994): 958-966.

\bibitem
{per}
Wallach, Hanna M., et al. "Evaluation methods for topic models." Proceedings of the 26th annual international conference on machine learning. 2009.

\bibitem
{data}
Dat Quoc Nguyen, Richard Billingsley, Lan Du, and Mark Johnson. Improving topic models with latent feature word representations. Transactions of the Association for Computational Linguistics, 3:299–313, 2015.

\end{thebibliography}
